VM-Centric Snapshot Deduplication for Converged Cloud Architectures

### 2014-07-19 snapshot_system/paper_analysis.tex
re

\section{Impact on Fault Isolation}
\label{sect:fault}
We  analyze  the impact of losing $d$ physical machines 
to the VM centric and oblivious approaches.  
There are two impacts to VC. 
1) Some PDS fingerprint lookup services do not respond.  As  a result, some duplicates
are not detected and deduplication efficiency suffers, but the overall systems can still
function well and fault tolerance is not affected.  As discussed in Section ~\ref{sect:architecture}, 
PDS index is distributed
among all machines in our implementation and thus a percentage of failed nodes
causes an increase in missed duplicates proportionally.
2) Some storage nodes do not  respond and file blocks on those machines are lost. The availability of
VM snapshots is affected and we analyze this impact as follows.

@@

As illustrated in Figure~\ref{fig:share}, we build a bipartite graph representing the
association from unique file system blocks to their corresponding VMs in two 
approaches. 
%We use a file system block rather than data chunk as our unit of failure
%because the underlying file system keeps file system blocks as its base unit of storage, and in
%the case of 64MB file system blocks  and 4KB chunks, there are 16K chunks per file block. For VM centric,
%we assign extra replication to the PDS blocks, while for VM oblivious, the replication
%degree is fixed.
For VC, each VM has an average number $N_1$ of non-PDS file system blocks
and  has  an average of  $N_2$ PDS file system blocks. 
Each non-PDS block is associated with only one VM.
% and  we denote that PDS blocks are shared by an average of $V_c$ VMs. 
By counting outgoing edges from VMs in Figure~\ref{fig:share}(a), we get:
\[
n* N_1   = \mbox{ Number of non-PDS file system blocks in VC.} 
\]

For VO, 
%each VM has an average of $N_o$ file system blocks
%and let $V_o$ be the average number of VMs shared by each file block.
by counting outgoing edges from VMs in Figure~\ref{fig:share}(b) with parameters defined in
Table~\ref{tab:symbol},  we have 
\[
n *N_o   =  V_o * \mbox{Number of file system blocks in VO}.
\]

>>>>

\section{Fault Tolerance and Snapshot Availability}
\label{sect:fault}
We  analyze  the impact of losing $d$ physical machines 
to the VM centric and oblivious approaches.  
There are two impacts to VC. 
1) Some PDS fingerprint lookup services do not respond.  As  a result, some duplicates
are not detected and deduplication efficiency suffers, but the overall systems can still
function well and fault tolerance is not affected.  As discussed in Section ~\ref{sect:architecture}, 
PDS index is distributed
among all machines in our implementation and thus a percentage of failed nodes
causes an increase in missed duplicates proportionally.
2) Some storage nodes do not  respond and file blocks on those machines are lost. The availability of
VM snapshots is affected and we analyze this impact as follows.

@@

As illustrated in Figure~\ref{fig:share}, we build a bipartite graph representing the
association from unique file system blocks to their corresponding VMs in two 
approaches. 
%We use a file system block rather than data chunk as our unit of failure
%because the underlying file system keeps file system blocks as its base unit of storage, and in
%the case of 64MB file system blocks  and 4KB chunks, there are 16K chunks per file block. For VM centric,
%we assign extra replication to the PDS blocks, while for VM oblivious, the replication
%degree is fixed.
For VC, each VM has an average number $N_1$ of non-PDS file system blocks
and  has  an average of  $N_2$ PDS file system blocks. 
Each non-PDS block is associated with only one VM.
% and  we denote that PDS blocks are shared by an average of $V_c$ VMs. 
By counting outgoing edges from VMs in Figure~\ref{fig:share}(a), we get:
$
n* N_1   = \mbox{ Number of non-PDS file system blocks in VC.} 
$

For VO, 
%each VM has an average of $N_o$ file system blocks
%and let $V_o$ be the average number of VMs shared by each file block.
by counting outgoing edges from VMs in Figure~\ref{fig:share}(b) with parameters defined in
Table~\ref{tab:symbol},  we have 
$
n *N_o   =  V_o * \mbox{Number of file system blocks in VO}.
$

### 2014-07-19 snapshot_system/paper_eval.tex
re

Table~\ref{tab:efficiency-comparison} shows the deduplication efficiency and per-machine memory usage for SRB and VC with different 
settings.
% <<<<<<< HEAD
% Our deduplication efficiency is defined as the percent of duplicate chunks
% which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
% The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
% is defined in Table~\ref{tab:symbol}. 
% =======
Deduplication efficiency is defined as the percent of duplicate chunks which are removed
compared to a perfect scheme which detects and removes  all duplicates. 
% so only global perfect deduplication can have 100\% efficiency.
% We also compare several PDS sizes chosen for VC.
%(see Table~\ref{tab:symbol} for definition of ``$\sigma=2\%$'')
%we allocate the space of distributed shared memory  to accommodate 2\%
%of data chunks shared among VMs, as defined in 
Notice $\sigma$ is the percentage of unique chunks selected in PDS.
With $\sigma =2\%$, Column 3 shows its 
%memory usage for PDS index lookup per machine is about 100MB per machine and  the 
deduplication efficiency can 
reach over 96\%. 
%When $\sigma=4\%$, Column 4 shows that the deduplication efficiency can reach 96.6\% while 
%more index space is allocated  per machine for  PDS fingerprint lookup.
The loss of efficiency in VC is caused by the restriction of the physical memory available
in the cluster for fast in-memory PDS index lookup. 
Memory usage per machine is low because each machine only hosts $1/p$  of  index for PDS 
plus some buffer space where $p$ is the number of physical machines. 
%In the extreme case if we put all the fingerprint into PDS 
%index ($\sigma=100\%$) then VC will have 100\% efficiency.
SRB in Column 5 can deliver up to 97.86\% deduplication efficiency, which is slightly better than VC.
Thus this represents a tradeoff as VC uses much less resource  and faster deletion.
%with a slight reduction in deduplication efficiency.
Memory usage per machine in SRB includes the Bloom filter space to access the on-disk index
and  cache for frequently or recently accessed chunk index.  
% SRB can deliver up to 97.935\% deduplication efficiency which is slightly better than VC.
% Thus this represents a tradeoff: VC provides better fault tolerance and fast
% approximate deletion with competitive (but slightly lower) deduplication
% efficiency.
% >>>>>>> 4dcd68612b052c0f890ed30361a9ed03771b5df1
%its loss of efficiency is caused by the routing of data chunks which restricts the search scope
%of duplicate detection.
%SRB provides slightly better deduplication efficiency than our VC approach, which we accept
%because we are rewarded by architecture-wise benefits such as fault-tolerance and fast 
%Though not our primary goal, this result does show that VC can remove competitive amount of duplicates.

@@

Table ~\ref{tab:resource_usage} shows that when  each machine conducts
backup one VM at a time, the backup of the entire
VM cluster completes in about 1.31 hours. Since there are about 25 VMs per physical machine, we could execute
more tasks in parallel at each machine. But adding more backup concurrency does 
not shorten the overall time
significantly in this case because of the controlled  disk read bandwidth usage.
When I/O throttling is not used, we will show below that processing multiple VMs concurrently 
does improve the throughput of backup.
%,  we can still process raw data at near 175 MB/s. If we consider the extreme case in which each machine has 25 VMs
%at 40GB size, our snapshot system can finish backing up all the VMs (1TB total) in 1.58 hours.

>>>>

Table~\ref{tab:efficiency-comparison} shows the deduplication efficiency and per-machine memory usage for SRB and VC with different 
settings.
% <<<<<<< HEAD
% Our deduplication efficiency is defined as the percent of duplicate chunks
% which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
% The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
% is defined in Table~\ref{tab:symbol}. 
% =======
Deduplication efficiency is defined as the percent of duplicate 
chunks removed, comparing to a perfect scheme which detects and removes  all duplicates. 
% so only global perfect deduplication can have 100\% efficiency.
% We also compare several PDS sizes chosen for VC.
%(see Table~\ref{tab:symbol} for definition of ``$\sigma=2\%$'')
%we allocate the space of distributed shared memory  to accommodate 2\%
%of data chunks shared among VMs, as defined in 
Notice $\sigma$ is the percentage of unique chunks selected in PDS.
With $\sigma =2\%$, Column 3 shows its 
%memory usage for PDS index lookup per machine is about 100MB per machine and  the 
deduplication efficiency can 
reach over 96\%. 
%When $\sigma=4\%$, Column 4 shows that the deduplication efficiency can reach 96.6\% while 
%more index space is allocated  per machine for  PDS fingerprint lookup.
The loss of efficiency in VC is caused by the restriction of the physical memory available
in the cluster for fast in-memory PDS index lookup. 
Memory usage per machine is low because each machine only hosts $1/p$  of  index for PDS 
plus some buffer space where $p$ is the number of physical machines. 
%In the extreme case if we put all the fingerprint into PDS 
%index ($\sigma=100\%$) then VC will have 100\% efficiency.
SRB in Column 5 can deliver up to 97.86\% deduplication efficiency, which is slightly better than VC.
Thus this represents a tradeoff as VC uses much less resource  and faster deletion.
%with a slight reduction in deduplication efficiency.
Memory usage per machine in SRB includes the Bloom filter space to access the on-disk index
and  cache for frequently or recently accessed chunk index.  
% SRB can deliver up to 97.935\% deduplication efficiency which is slightly better than VC.
% Thus this represents a tradeoff: VC provides better fault tolerance and fast
% approximate deletion with competitive (but slightly lower) deduplication
% efficiency.
% >>>>>>> 4dcd68612b052c0f890ed30361a9ed03771b5df1
%its loss of efficiency is caused by the routing of data chunks which restricts the search scope
%of duplicate detection.
%SRB provides slightly better deduplication efficiency than our VC approach, which we accept
%because we are rewarded by architecture-wise benefits such as fault-tolerance and fast 
%Though not our primary goal, this result does show that VC can remove competitive amount of duplicates.

@@

Table ~\ref{tab:resource_usage} shows that when  each machine conducts
backup one VM at a time, the entire cluster backup 
completes in 1.31 hours. Since there are about 25 VMs per physical machine, we could execute
more tasks in parallel at each machine. But adding more backup concurrency does 
not shorten the overall time
significantly in this case because of the controlled  disk read bandwidth usage.
When I/O throttling is not used, we will show below that processing multiple VMs concurrently 
does improve the throughput of backup.
%,  we can still process raw data at near 175 MB/s. If we consider the extreme case in which each machine has 25 VMs
%at 40GB size, our snapshot system can finish backing up all the VMs (1TB total) in 1.58 hours.
